---
title: "car_viz_comments"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#car_viz.R
```{r}
# Loading the tidyverse packages.

library(tidyverse)

# Call built-in data mtcars.

data(mtcars)

# Select only car models where mpg<30

mtcars_mpg2 <- mtcars[mtcars$mpg < 30,]

# Look the first six lines of the mtcars_mpg2.

head(mtcars_mpg2)

# Reduce the variables to mpg, cyl, disp, hp, gears

mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]


# Read the R file hand_functions.R so that it can be used
# Notice that with echo = TRUE 

source(file = "hand_functions.R", echo = TRUE)


# Now use the function from hand_functions.R

sp_out <- sum_special(mtcars_mpg2)


#library(esquisse)
 
#esquisser(data = mtcars_mpg2, viewer = "browser")



ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()


# note that this box plot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?


ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")

# try to exchange the size of data to a factor, then we can use the function esquisse()
# to plot a boxplot.
```

#Comments:
From this very simple exploration, I learned how to create an organization with the repositories. I also learned how to upload my rmd, the output html and pdf file to github by R. It can provide a method to share my codes with others in the future, which is very interesting.

For the R codes part, I learned how to reduce the variables of a data frame, how to use function esquisse() to plot. 




